Title

### 2012-05-21 inc/external_forces/external_forces.tex
fixed typo

\ref{eq:potential_integral} is the entry point for the internal Coulombing repulsion force; since both potentials and integrals are linear, one may add additional potentials so that it becomes
\begin{equation}
  \begin{split}
    \Phi(\vec{r};t) \rightarrow & \int d\vecprime{r} \left( V(\vec{r} - \vecprime{r}) + \sum V_{ext}(\vec{r}) \right) n(\vecprime{r}; t) \\
    = & \int d\vecprime{r} V(\vec{r} - \vecprime{r}) n(\vecprime{r}; t) + \sum \int d\vecprime{r} V_{ext}(\vec{r}) n(\vecprime{r}; t) \\
    = & \Phi(\vec{r};t) + \Phi_{ext}(\vec{r};t)
  \end{split}
\end{equation}
This form of $\Phi(\vec{r};t)$ can be substituted into the definition of $K^{force}$ (\ref{eq:Kforce}), again in the basis defined in \ref{eq:coordinate_vector} 
\begin{equation}
  \begin{split}
    K^{force}_{ij} \rightarrow & \frac{1}{N} \int u_i u_j \frac{\partial f}{\partial \vec{p}} \frac{\partial}{\partial \vec{r}} \left( \Phi(\vec{r};t) + \Phi_{ext}(\vec{r};t) \right) d\vec{r} d\vec{p} \\
    \equiv & K^{int}_{ij} + \sum K^{ext}_{ij}
  \end{split}
\end{equation}
where $K^{int}$ is simply the old $K^{force}$. Noting that the spatial derivative of a potential is just the force, we can now define the matrix contributed by each external force is given by
\begin{equation}
  K^{ext}_{ij} = \frac{1}{N} \iint u_i u_j \left [ \frac{\partial}{\partial \vec{p}} f(\vec{r}, \vec{p}; t) \right ] \cdot \vec{F}_{ext}\;d^{3}x\,d^{3}p
\end{equation}
Finally, the general form of \ref{eq:gaussian_integral_dt_k} for (possibly multiple) external force ($\vec{F}_{ext}$) contributions is now
\begin{equation}
  \frac{\partial}{\partial t} A^{-1}_{ij} = K^{flow}_{ij} + K^{int}_{ij} + \sum K^{ext}_{ij}
\end{equation}

>>>>

\ref{eq:potential_integral} is the entry point for the internal Coulombic repulsion force; since both potentials and integrals are linear, one may add additional potentials so that it becomes
\begin{equation}
  \begin{split}
    \Phi(\vec{r};t) \rightarrow & \int d\vecprime{r} \left( V(\vec{r} - \vecprime{r}) + \sum V_{ext}(\vec{r}) \right) n(\vecprime{r}; t) \\
    = & \int d\vecprime{r} V(\vec{r} - \vecprime{r}) n(\vecprime{r}; t) + \sum \int d\vecprime{r} V_{ext}(\vec{r}) n(\vecprime{r}; t) \\
    = & \Phi(\vec{r};t) + \Phi_{ext}(\vec{r};t)
  \end{split}
\end{equation}
This form of $\Phi(\vec{r};t)$ can be substituted into the definition of $K^{force}$ (\ref{eq:Kforce}), again in the basis defined in \ref{eq:coordinate_vector} 
\begin{equation}
  \begin{split}
    K^{force}_{ij} \rightarrow & \frac{1}{N} \int u_i u_j \frac{\partial f}{\partial \vec{p}} \frac{\partial}{\partial \vec{r}} \left( \Phi(\vec{r};t) + \Phi_{ext}(\vec{r};t) \right) d\vec{r} d\vec{p} \\
    \equiv & K^{int}_{ij} + \sum K^{ext}_{ij}
  \end{split}
\end{equation}
where $K^{int}$ is simply the old $K^{force}$. Noting that the spatial derivative of a potential is just the force, we can now define the matrix contributed by each external force is given by
\begin{equation}
  K^{ext}_{ij} = \frac{1}{N} \iint u_i u_j \left [ \frac{\partial}{\partial \vec{p}} f(\vec{r}, \vec{p}; t) \right ] \cdot \vec{F}_{ext}\;d^{3}x\,d^{3}p
\end{equation}
Finally, the general form of \ref{eq:gaussian_integral_dt_k} for (possibly multiple) external force ($\vec{F}_{ext}$) contributions is now
\begin{equation}
  \frac{\partial}{\partial t} A^{-1}_{ij} = K^{flow}_{ij} + K^{int}_{ij} + \sum K^{ext}_{ij}
\end{equation}
